---
title: "MP Tweets Dataset Notebook"
output: html_notebook
---

# Pulling British MPs' Tweets

The aim of this mini-project is to create a dataset of British MPs' tweets. In order to do this, an academic

## Set-up

In order to run the code, an academic developer licence is required to access Twitter's API.

Once you have an academic licence:

-   Copy your bearer token

-   Load the `academictwitteR` package

-   Run the command `set_bearer()` and follow the instructions

-   They involve making a file called `.Renviron` in the root directory and typing:

    -   `TWITTER_BEARER=AAAA…`, where `AAAA…` is your own bearer token

-   You can also set your bearer token manually, but this is less secure because it might appear in `.Rhistory` files or scripts. This is especially a problem if they are shared files.

The rest of the code can be run from this repository

## Code

```{r}
if (!require("here")) install.packages("here")
source(here("code", "01_packages.R"))
```

Helpfully, [Michael Keith](https://www.michaelkeith.co.uk/) has created a [online dashboard](https://www.politics-social.com/) of British MPs' Twitter activity. On the website, there are `.csv` files which allow us to pull MPs' usernames. Run the following script:

```{r}
source(here("code", "1_pull-latest-MPs.R"))
```
